Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Fix fig 5 caption.

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup
    is active for decision index $i\in\{0,1,5\}$, which correspond to
    states such that $r_Z=\rzup$.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. More
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
\end{equation}
time steps, where $H_x$ is closed-loop transfer function for the
$x$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.

>>>>

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. More
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
\end{equation}
time steps, where $H_x$ is closed-loop transfer function for the
$x$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.
